Placeholder Title... Something About Delegating Quantum Computations

### 2019-10-12 longoutput.tex
Clarify weights definition
Fix indentations
Fix typo in algorithm
Add work on amplification
Write down new flow of logic

\begin{algorithm}
	\caption{Check for ground state}
	\label{AlgGroundStateCheck}
	\begin{algorithmic}[1]
		\Require $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$
		\Procedure{GroundStateCheck}{$\ket\phi$}
		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
		\State $p_S=\frac{|d_S|}{D}$
		\State $\widetilde{S}\gets$ Pick weighted using $p_S$
		\State $\lambda_{\widetilde{S}}\gets$ Measure $\ket\phi$ in the $\widetilde{S}$ basis
		\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}
		\State Accept
		\Else
		\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\begin{theorem}
	Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
	\begin{itemize}
		\item has $t$ terms
		\item acts on $q$ qubits
		\item Ground state $0$...?
		\item Something something $\frac{3}{4}$?
	\end{itemize}
	Then, with the input, if honest is $n=O(\poly(t))$... TODO
\end{theorem}
\begin{proof}
	Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Delta$ for $i\ne1$, where $\Delta=\Omega\left(\frac{1}{\poly(t)}\right)$. We now decompose the input in this basis. Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices.
	$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$
	Fix $\delta<2\Delta$ and let $B=\frac{1}{2}-\delta$. Partition the multi-indices into three types.
	$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
	$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq 2\delta n}$$
	$$\mathcal{I}_2=\mathcal{I}\setminus\mathcal{I}_1\setminus\mathcal{I}_3$$

	Apply \autoref{AlgGroundStateCheck} to every register of $\ket{\phi_1^{\otimes n}}$. By Chernoff bound, there is overwhelming (as $n$ grows) probability that more than $Bn$ registers are accepted. On the other hand, take $J\in\mathcal{I}_3$ and do the same to every register of $\ket{\phi_J}$. By Chernoff bound, there is overwhelming probability that less than $Bn$ registers are accepted.

	Now also define the following.
	$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
	$$b=\sum_{J\in\mathcal{I}_2}\beta_J\overline{\beta_J}$$
	$$c=\sum_{J\in\mathcal{I}_3}\gamma_J\overline{\gamma_J}$$

	Then apply \autoref{ThmXZCheck}. By the linearity of expected values, the number of accepted qubits should be around...
	TODO Does this actually work?

>>>>

\begin{algorithm}
	\caption{Check for ground state}
	\label{AlgGroundStateCheck}
	\begin{algorithmic}[1]
		\Require $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$
		\Procedure{GroundStateCheck}{$\ket\phi$}
		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
		\State $p_S\gets\frac{|d_S|}{D}$
		\State $\widetilde{S}\gets$ Pick weighted using $p_S$
		\State $\lambda_{\widetilde{S}}\gets$ Measure $\ket\phi$ in the $\widetilde{S}$ basis
		\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}
		\State Accept
		\Else
		\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\begin{theorem}
	Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
	\begin{itemize}
		\item has $t$ terms
		\item acts on $q$ qubits
		\item Ground state $0$...?
		\item Something something $\frac{3}{4}$?
	\end{itemize}
	Then, with the input, if honest is $n=O(\poly(t))$... TODO

	Client sends $N$ copies...
\end{theorem}
\begin{proof}
	Let $\set{\ket{\phi_1},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$.
	Then $\ket{\phi_1}$ has eigenvalue $\lambda_1=0$, and $\ket{\phi_j}$ has eigenvalues $\lambda_j\geq\tilde\lambda$ for $j>1$.

	Consider
	$$\sum_{j=1}^nH^j$$
	Where $H^j$ denotes $H$ acting on the $j$th qubit. So it has eigenbasis $\ket{\phi_J}$ for some multi-index $J$ with corresponding eigenvalue
	$$\sum_{i\in J}\lambda_i$$

	Now fix $\delta$ and define $n_c=\delta N$, $n_b=2n_c=2\delta N$.
	If more than $n_b$ registers reject, then with overwhelming probability bad state...
	Otherwise eigenvalue < $n_c$?

	Then done?
